---
title: "hectimetables - runDemo"
output: rmarkdown::html_vignette
description: >
  Learn how to open the shinyApp specially created to Business Analytics students 
  in the Master in Management at HEC Lausanne, year 2020-2022 using `runDemo()`.
vignette: >
  %\VignetteIndexEntry{hectimetables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Installing the package

The package required is on GitHub, run the following code in your R console to load it.

```{r}
devtools::install_github("ptds2021/project--G2")

# Update packages (if you want to skip this step, just enter 3 - none)

library("hectimetables")

hectimetables::runDemo()
```

# Opening the app

To open the app (either on R or in your internet browser), simply run this command.

```{r}
hectimetables::runDemo()
```

## Semesters' choice

There are three tabs, for the three semesters of classes of the Master. \
You can navigate across them by simply clicking on it at the top of the page.

## Initial timetable suggestion

To display an initial timetable, click on "Suggest" on the sidebar panel.

You have the choice to either view, by moving across tabs in the main panel:

-   a textual summary of the selected classes

-   a visual representation of the selected classes

Note that the mandatory classes of this master are pre-selected and will be included in the suggested timetable even if de-selected them from the list of preferred classes.

## User's preferences

You can of course also input your preferences to have a personalized timetable:

-   how many credits you want to obtain at least (total credits) ?

-   how many credits you want to do in the Business Analytics track (core credits) ?

-   how many credits you want to do as elective classes (non mandatory ones) ?

-   which days (divided in morning and afternoon) you want to have class ?

## Issues 

Note that if no timetable is displayed, it simply mean your preferences could not be satisfied. In this case, you need to either choose more days and remove conflicting classes.

A good advice is always to start from the first generated timetable. \
Otherwise, to only add a few favorite classes and then scale it up.

# Why we like this package

As former BA students at HEC Lausanne, we struggled to create a suitable timetable which would satisfy all constraints. Here, as part of a Programming class, we coded a possible solution to our problem in a ShinyApp. We made it available, so other students could benefit from it.
